Races with hyper3 objects

### 2024-01-21 inst/race3.Rmd
consistentification
rewording

---
title: "Races with hyper3 objects"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

(takes about an hour to process without cache).  To cite the `hyper2`
package in publications, please use @hankin2017a.  Consider a race in
which there are six runners 1-6 but we happen to know that three of
the runners (1,2,3) are clones of strength $p_a$, say, two of the
runners (4,5) have strength $p_b$, and the final runner (6) is of
strength $p_c$.  The runners race and the finishing order is:

@@

Above we see strong evidence to reject the hypothesis that
$p_a=p_b=p_c=\frac{1}{3}$.  We may also test the hypothesis that the
strength vector is equal to its true value:

>>>>

---
title: "Races with hyper3 objects"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

(takes about an hour to process without cache).  To cite the `hyper2`
package in publications, please use @hankin2017.  Consider a race in
which there are six runners 1-6 but we happen to know that three of
the runners (1,2,3) are clones of strength $p_a$, say, two of the
runners (4,5) have strength $p_b$, and the final runner (6) is of
strength $p_c$.  The runners race and the finishing order is:

@@

Above we see a $p$-value of $<10^{-6}$, strong evidence to reject the
hypothesis that $p_a=p_b=p_c=\frac{1}{3}$.  We may also test the
hypothesis that the strength vector is equal to its true value:
